\begin{itemize}
	\item \textbf{First Tech Challenge (FTC) Robotics, Co-Captain, Software Lead} (9th–11th Grade): Co-captain for a community robotics team with fully custom robot design and software. Won multiple local awards for software and hardware innovation, becoming a regional and state finalist alliance team and ranked top-30 globally for the autonomous section. Mentored over 200 students across various platforms.

	\item \textbf{Simply Stir Research Project} (9th Grade): Completed independent research on harvesting thermal energy to power a self-stirring pot. Won 1st place in Engineering Technology at regional science fair, within the top 9 overall projects (\$300). Also won US Metric Association Best SI Units and US Air Force Certificate of Recognition. Advanced as a finalist to the International Science and Engineering Fair (ISEF).

	\item \textbf{Gait Guardian Research Project} (10th Grade): Completed independent research on using machine learning and signal processing for Parkinson’s Disease patients. Won 1st place in Systems Software at regional science fair and 2nd Grand Prize Overall (\$400). Won TI Best Computing Project, and advanced as an ISEF finalist. Won 3rd in Robotics and Intelligent Machines at ISEF (\$1200).

	\item \textbf{School Science Fair Club, Officer} (10th–11th Grade): Served as Underclassmen President and later as Vice-President of the school’s science fair club, organizing meetings, mentoring new members, and leading STEM outreach events in the local community. Conducted biweekly lunch meetings to guide students through project ideation, research methods, and presentation skills.

	\item \textbf{Speech and Debate} (9th–11th Grade): National (NSDA) and State Quarterfinalist in Impromptu Speaking; National Octofinalist in Extemporaneous Commentary. Won local and regional tournaments in Duo Acting and Extemporaneous Speaking. Developed a custom timer utility and Congress presiding officer app used by state and national competitors.

	\item \textbf{Keyboardist for Local Band} (9th–11th Grade): Performed as a self-taught keyboardist in a local band with ticketed shows and millions of views on YouTube. Donated performance revenue to charity, raising over \$200,000 to support medical expenses. Volunteered more than 100 hours and earned the President’s Volunteer Service Award (Silver).

	\item \textbf{Original Music Arrangement and Composition} (9th–11th Grade): Composed and arranged original film music using self-taught skills in music production, keyboard, and bass guitar. Collaborated with local artists and a renowned Tamil film music composer.

	\item \textbf{NSDA Certified Debate Judge} (9th–11th Grade): Judged local Middle School debate tournaments in a fair and unbiased manner. Judged events include Extemporaneous Speaking, Congressional Debate, Public Forum Debate, Duo Interpretation, Dramatic Interpretation, and Original Oratory.

	\item \textbf{ACE Tutoring Officer} (10th–11th Grade): Tutoring officer for Calculus and Math in 10th grade, and Chemistry in 11th grade. Published study material and practice tests for studying students, and hosted live review sessions for live Q\&A. As officer, managed other guides to ensure that resources are top-quality.

	\item \textbf{NHS Technology Officer} (11th Grade): Served as Technology Officer for the largest NHS chapter worldwide. Built a React-based full-stack web portal to streamline member management, event coordination, and service hour tracking using QR codes and a Firebase database.

	\item \textbf{National Honor Society (NHS) Member} (10th–11th Grade):

	\item \textbf{Math Club} (9th–11th Grade): Competed in local math competitions, including AMC 10/12 and AIME (1× qualifier).

	\item \textbf{Founder of School’s Cricket Club} (11th Grade): Founded and organized the school’s first competitive cricket club, coordinating practices, matches, and logistics. Expanded participation to over 30 members and introduced 15 new players to the sport.

	\item \textbf{Owner of Class Discord Server} (9th–11th Grade): Founded and managed a class Discord server for studying and resource sharing. Supported over 150 active members with structured subject channels, live study sessions, and teacher-supported moderation.
\end{itemize}