% Describe any paid or volunteer work experience and include your responsibilities. Provide examples of strong work ethic (such as no unexcused
% absences or reprimands, completes assigned tasks, works well with others, etc). If no formal work experience, provide detailed description of the
% effort involved in a major school project (include grade awarded, teamwork involved, how you overcame challenges).



\begin{enumerate}
	\item I have been working for a local ticketed nonprofit band for three years as a Keyboard player.
	      As a musician, I am expected to fully practice my parts individually to a level of near-mastery. Each concert will demand at least
	      3-4 section practices, where I have to coordinate with other musicians in my section to ensure that we are in sync.
	      Teamwork is a relative struggle, and each of us has differing opinions on the best way to play a specific piece. I
	      have learned to offer my input respectfully and to avoid heated arguments by focusing on the music itself. Full band
	      practices are also held for each performance, where attendance is absolutely mandatory. Each musician contributes to the final song,
	      and missing a practice would lead to a lack of cohesion in the final performance. In this band, I ensure that I attend every
	      practice and performance, and I have never had an absence or reprimand. Although our final work is paid through ticket sales,
	      all revenue is donated to local charities, and I take pride in knowing that my work is helping those in need.
	\item For three years, I have been an NSDA certified judge, judging Middle School Debate tournaments in my local area.
	      My duties include evaluating debaters on argumentation, speaking style, and providing constructive feedback to help them improve.
	      Each tournament lasts a full day, and I am expected to judge numerous rounds (at times six or more) with minimal breaks.
	      Not only do I have to maintain focus and attention throughout the day, but I also have to judge impartially,
	      as not doing so would completely undermine the integrity of the tournament. After updating availability, I cannot
	      drop out of a tournament or a round, as the tournament relies on a planned agenda to run smoothly. My greatest hurdle has
	      been setting aside my own political bias, as I have heard numerous speeches and arguments supporting views I both
	      strongly agree and disagree with. I overcame this challenge by shifting the criteria at those times to the efficacy of argument
	      and speaking style, rather than the content itself.
	      Outside of judging I am responsible for for writing topics for each tournament, reviewing all updated rules and topics,
	      and reporting behavioral incidents. Overall, I have judged over 50 rounds of debate without a single absence, and I
	      hope that I have been a fair adjudicator of the activity I love.
	\item For the last three years, I have been tutoring in math and science on and off. I initially started tutoring
	      competition math to middle schoolers through my own paid company I had started when in middle school.
	      The tutoring service was unique, offering a problem-based approach instead of a topic-based approach, prioritizing
	      problem-solving skills and critical thinking. As I was the
	      only person running the tutoring service, I had to find my own clients, schedule sessions, and prepare lesson plans.
	      Halfway through my ninth grade, I only had one customer, so I decided to pivot my skills to instead offer free tutoring
	      to my peers in my high school. Through my school's ACE tutoring program and my own study Discord server,
	      I have been able to help numerous students in
	      Calculus, Chemistry, and even history. Each session requires significant preparation, as I have to explain
	      the concepts in an intuitive manner that struggling students can understand. So far, I have received positive feedback
	      from my students, and I always prioritize their learning and understanding above all else.
	\item From halfway in my 9th grade to now, I have started, owned, and am fully maintaining a Discord study server for our school's
	      student class of 2027. As the owner, I am fully responsible for a managing a team of 8 voted moderators, and I have
	      to ensure that everybody's voices are heard. As the server is run through Discord, arguments and disagreements can
	      easily escalate, so I have to step in as a neutral party to mediate and resolve conflicts. It was through these Discord
	      "blow-ups" that I started learning how to be a better leader and work with others. I have poured over 300 hours into
	      this server, managing over 100 active members. Housing over 50\% of the class (at its peak) was a daunting task, and I
	      had to deal with revolts and mass exodus of members multiple times. From arguments about the "wetness of water" to
	      kicking me out of my own server, I have seen and managed all of these conflicts. Now, our server is a stable and 
          thriving community, with valuable study resources, popular group study calls, and constant member engagement through 
          general (and of-topic) text channels.
	\item % NHS officer work!!.. AYNY VOLUNTEER OR PAID WORK
	\item % Robotics team work?
	\item % Science fair club officer work?
	\item % Cricket club work?
	\item
\end{enumerate}